---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE,
  warning = FALSE
)
```

# coheRence

<!-- badges: start -->
<!-- badges: end -->

The goal of **coheRence** is to calculate average coherence values for individual building polygons within a user-defined region. By utilizing pre-processed coherence maps (e.g., from Sentinel-1) and building geometries (e.g., from OpenStreetMap), the package clips spatial data and computes mean coherence values per building to assess its structural status.

### Key Features
* **Data Output**: Automatically saves results as GeoPackage (`.gpkg`) and `.png` files for seamless integration into GIS environments and easy reporting.
* **Workflow Integration**: Implements customizable classification schemes to categorize damage levels.
* **Visualization**: Generates colored plots and time-series graphs to provide a clear overview of analyzed data.

### Use Cases
This analysis provides a rapid method to combine coherence loss estimation with built-up areas. It is particularly valuable for monitoring areas affected by **armed conflicts** or **natural disasters**. The exported data can be used for further spatial analysis of damage patterns, either for a specific event or as a longitudinal time series.

> [!IMPORTANT]
> This package is designed for post-processing and analysis. It is **not** capable of downloading raw data or processing initial SAR scenes (e.g., from SLC to Coherence).

## Installation

You can install the development version of coheRence from [GitHub](https://github.com/) with:

``` {r installation}
# install.packages("pak")
pak::pak("andeelia/coheRence")
```

## Workflow

The complete workflow is shown here:

### Load And Clip

The first function takes .tif files from a set path, converts them to a pre-defined CRS and clips them with building polygons.

```{r load_and_clip}
library(coheRence)
library(terra)
library(sf)
library(tictoc)

#define personal variables
path <- '/home/andeelia/Documents/GitHub/package_test/raw_data/'
gaza_crs <- "EPSG:32636" 
final_dir <- '/home/andeelia/Documents/GitHub/package_test/clipped_data/'
buildings <- '/home/andeelia/Documents/GitHub/package_test/raw_data/Gaza_Stripe_buildings.shp'

#call first function to prepare further processing steps
clips <- load_and_clip(data_path = path, target_crs = gaza_crs, buildings_path = buildings, save_clips = TRUE, project_path = final_dir)
```

The result of this function is a list consisting of three things.

- A list of SpatRaster objects, clipped to the building outlines
```{r clips1}
plot(clips[[1]][[1]])
```

- A spatial DataFrame including the buildings clipped to the extent of the input images
```{r clips2}
head(clips[[2]])
```

- A numerical value, representing the number of input images
```{r clips3}
print(clips[[3]])
```

### Coherence Calculation
By assigning the results from `load_and_clip()` to variables, they can be used in the following function:

```{r coh_calc}
library(coheRence)
library(terra)
library(sf)
library(tictoc)

#assign results from load_andclip
clipped_raster <- clips[[1]]
clipped_buildings <- clips[[2]]

#call second function to analyse your dataset
coh_results <- coh_calc(rast_data = clipped_raster, buildings = clipped_buildings, target_crs =  gaza_crs, project_path = final_dir)

```

The result of this function looks like this:

```{r coh_results}
head(coh_results)
```

### Classified Plots
As you can see, the calculated results are added to the end of the DF.
Finally, two plots will be created by calling classified plots:

```{r plots, fig.show = 'hold'}
library(coheRence)
library(tictoc)
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)
library(patchwork)

#assign result from load_and_clip
image_count <- clips[[3]]

#call function to plot graphs
classified_plots(coh_df = coh_results, number_of_images = image_count, project_path = final_dir)

```

## Citation
To cite **coheRence** in publications, please use:

> Andersch, E. (2026). coheRence: Coherence loss analysis based on building polygons and coherence maps. R package version 0.1.0. URL: https://github.com/andeelia/coheRence

Alternatively, you can run `citation("coheRence")` in R to get the BibTeX entry.